#Packages Needed
```{r}
library(dplyr)
library(ggplot2)
library(reshape)
```

#Enter the path to the TAIR10 GTF, your gene list, and your bedgraph in likes 11, 12 and 13 respectively 
##This assumes there are no headers in your data, the first line of the file is data
###noramlization will be the eventual y-axis lab
###start and end are start and end positions from the TSS
```{r}
gene_List <- read.delim("/Path/to/GeneList", header = FALSE)
Tair10 <- read.delim("/Path/to/TAIR10/GTF", header = FALSE)
bedgraph <- read.delim("/Path/to/bedgraph", header = FALSE)
normalization <- "y axis label"
start <- #negative upstream value
end <- #positive downstream value
```

#Generate Position file around your genes eventually used for graphing. Default is 3kb from the gene TSS

```{r}
genes.only <- c(substr(Tair10$V9, 34,42))
Tair10$geneID <- genes.only
transcripts <- subset(Tair10, V3 == "transcript")
gene_info <- subset(transcripts, geneID %in% NPR1_4hours$NearestPromoterID)
gene_info$V9 <- NULL

gene_info <- gene_info %>%
  arrange(geneID, V4) %>%
  filter(duplicated(geneID) == FALSE)

genes_plus <- subset(gene_info, V7 == "+")
genes_minus <- subset(gene_info, V7 == "-")
genes_plus.pos <- as.data.frame(cbind(genes_plus$V1, genes_plus$V4+start,  genes_plus$V4+end))
genes_minus.pos <- as.data.frame(cbind(genes_minus$V1, genes_minus$V5+end,  genes_minus$V5+start))
```

#Generate the positions that will be extraxted from the bedgraph file
```{r}
filter_plus <- as.data.frame(rep(genes_plus.pos$V1, each = length(genes_plus.pos$V2[1]:genes_plus.pos$V3[1])))
mat <- matrix(ncol = length(genes_plus.pos$V2[1]:genes_plus.pos$V3[1]), nrow = nrow(genes_plus.pos))
for( i in 1:length(genes_plus.pos$V1)) {
     nt <- genes_plus.pos$V2[i]:genes_plus.pos$V3[i]
     mat[i,] <- c(nt)
}
mat <- t(mat)
mat_collapse <- c(mat)
filter_plus$start <- mat_collapse
filter_plus$RelPos <- rep(start:end, nrow(genes_plus.pos))
colnames(filter_plus)[1] <- "chr"
filter_minus <- as.data.frame(rep(genes_minus.pos$V1, each = length(genes_minus.pos$V2[1]:genes_minus.pos$V3[1])))
mat <- matrix(ncol = length(genes_minus.pos$V2[1]:genes_minus.pos$V3[1]), nrow = nrow(genes_minus.pos))
for( i in 1:length(genes_minus.pos$V1)) {
     nt <- genes_minus.pos$V2[i]:genes_minus.pos$V3[i]
     mat[i,] <- c(nt)
}
mat <- t(mat)
mat_collapse <- c(mat)
filter_minus$start <- mat_collapse
filter_minus$RelPos <- rep(start:end, nrow(genes_minus.pos))
colnames(filter_minus)[1] <- "chr"
```

#Extract the score of the bedgraph files and graph the average
##The y-axis can be changes based
```{r}
plus_score <- inner_join(filter_plus, bedgraph, by = c("chr"= "V1", "start" = "V2"))
minus_score <- inner_join(filter_minus, bedgraph, by = c("chr"= "V1", "start" = "V2"))
scores<- rbind(plus_score, minus_score)

graphing_df <- aggregate(V4 ~ RelPos, data=scores, mean)

ggplot(graphing_df, aes(x = RelPos, y = V4)) +
  geom_line(size = 0.5) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), legend.position = c(0.96, 0.8), legend.text = element_text(size = 12), legend.key=element_blank()) +
  xlab(expression("Position from TSS")) +
  theme(axis.text = element_text(size = 14)) +
  theme(axis.title = element_text(size = 20)) +
  ylab(normalization) +
  guides(colour = guide_legend(override.aes = list(size=2)))
```
